\chapter{Research Questions}

The main objective is to develop the PyPSA-Eur energy system model to account for offshore geographic conditions in the Baltic Sea Region, specifically sea bed geography and bathymetry. The influence of this adaptation on the energy system is studied by focusing on three key components: offshore wind farms, hydrogen systems, and grid infrastructure. This study is motivated by the endeavours of the Dutch engineering firm Witteveen+Bos.\\

The Baltic Sea's bed geography and bathymetry conditions are considered in this study because the conditions are expected to affect the installation costs of the offshore wind farms, hydrogen systems and infrastructure. The geography and bathymetry conditions are expected to influence the installation costs of offshore wind turbines and hydrogen systems because the support structure type is expected to depend on these conditions. The infrastructure costs depend mainly on the offshore wind farm and hydrogen system locations, which are expected to change in the optimisation problem of the energy system model that accounts for these offshore conditions.\\

The Dutch engineering firm Witteveen + Bos is interested in this study because the Energy System Studies group is actively working with PyPSA-Eur. Additionally, the firm has a branch office in Latvia and intends to contract future renewable energy projects in the Baltic Sea Region, including offshore wind farms, hydrogen systems and infrastructure.\\


\textbf{Main Research Question:}
\begin{quote}
    \emph{How can the offshore conditions be accounted for in modelling the energy system of the Baltic Sea Region?}
\end{quote}

\noindent \textbf{Subquestions:}
\begin{enumerate}
    \item \emph{How do the offshore conditions influence the predicted offshore wind farm distribution in modelling the energy system of the Baltic Sea Region?}
    \item \emph{How do the offshore conditions influence the predicted offshore hydrogen system distribution in modelling the energy system of the Baltic Sea Region?}
    \item \emph{How do the offshore conditions influence the predicted electricity and hydrogen infrastructure in modelling the energy system of the Baltic Sea Region?}
\end{enumerate}
